### 2016-07-18 generic.tex
cheers
replies to comments...

\begin{definition}
A (randomized) \emph{data structure} is a pair of algorithms $(\Rep, \Qry)$
parameterized by a collection $\mathcal{S}$ of subsets of~$U$ and a collection
of supported queries $\mathcal{Q}$ and having the following syntax:
\begin{itemize}
\item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
and outputting a pair of values $(\pub, M)$.
\item $\Qry$ is a deterministic algorithm that takes as input $\pub, M$,
and a query $q\in \mathcal{Q}$, and returns an answer~$a$.
\end{itemize}
A data structure is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
all $q \in \mathcal{Q}$ it holds that
\begin{eqnarray}
\Pr[(\pub, M) \leftarrow \Rep(S) : \Qry(\pub, M, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
\end{eqnarray}
where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
The \emph{size} of a data structure is the maximum length of any~$M$ that can be
output by $\Rep$.
\end{definition}

Our treatment of $\pub, M$ is not symmetric, since we only count $M$ against the size
of the data structure. When we define security
we may give the attacker $\pub$ but not~$M$, and in that case the data structure cannot
trivially make everything part of~$\pub$. \tsnote{Is the idea that
  anything that is secret is part of~$M$?  For example, if the scheme
  uses public hash functions to populate a bit-array, and then a
  secretly-keyed blockcipher to encipher the array; the
  blockcipher key is encoded in~$M$?  This may cause some issues in
  the security defintions, i.e.\ whether we can give~$M$ to the
  attacker or not. } \tsnote{By the way, I'm coming around to the
  viewpoint that it is fair to include in the ``size'' of the
  representation any secret information.  In makes more difficult
  comparisons to classical lower-bounds (which [NY] makes, incorrectly
IMO), but it does seem fair to say ``this is how many bits of memory
you need to allocate to represent this set \emph{securely}.''  }

It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
array in the usual way; a natural possibility is to set $\pub = (h_1, \ldots, h_k)$ and
to let $M$ be the bit array.  \tsnote{If $\mathcal{Q}=U$ and we use the
  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
  both correctness and soundness?  If so, I don't see how this
  captures the classical BF, which requires $\epsilon=0$ for one kind
  of error, but allows $\epsilon>0$ for the other. }

@@

The notion of FP-security defined above captures the fp-prv notion for Bloom filters
if we put the hash
functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
notion if we put the hash function in~$\pub$. \tsnote{Except that the win condition allows both
false-positives and false-negatives, given the correctness requirement
in the syntax.} It captures the fp-bb-pub notion in the
random-oracle model.

@@

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\pub$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{How will the adversary know that a query satisfies
  this in (say) the case of the classical BF?  We can, of course,
enforce it in the experiement, but then our resource accounting risks
overcounting the number of queries.} \tsnote{Also, we need that, in general, $\pub$ itself
does not leak information about~$S_0$ vs.\ $S_1$. }
\end{enumerate}

>>>>

\begin{definition}
A (randomized) \emph{data structure} is a pair of algorithms $(\Rep, \Qry)$
parameterized by a collection $\mathcal{S}$ of subsets of~$U$ and a collection
of supported queries $\mathcal{Q}$ and having the following syntax:
\begin{itemize}
\item $\Rep$ is a randomized algorithm taking as input $S \in \mathcal{S}$,
and outputting a pair of values $(\pub, M)$.
\item $\Qry$ is a deterministic algorithm that takes as input $\pub, M$,
and a query $q\in \mathcal{Q}$, and returns an answer~$a$.
\end{itemize}
A data structure is \emph{$\epsilon$-correct} if for all $S \in \mathcal{S}$ and
all $q \in \mathcal{Q}$ it holds that
\begin{eqnarray}
\Pr[(\pub, M) \leftarrow \Rep(S) : \Qry(\pub, M, q) \neq q(S)] \leq \epsilon, \label{eqn:correctness}
\end{eqnarray}
where $q(S)$ denotes the correct answer to the query $q$ on the set~$S$.
The \emph{size} of a data structure is the maximum length of any~$M$ that can be
output by $\Rep$. \tsnote{How does one define the length of~$M$,
  without knowing what kind of object it is (or demanding it be
  bit-length, relative to some implicit encoding into bitstrings)?
  Also, why take the max?  Why not just the length of~$M$, whatever it
happens to be?}\jnote{I was assuming that $M$ is a bitstring. One can talk
about the length of $M$ in some run of the algorithm, but when you want to talk
about how well the data structure as a whole performs, taking the max is one natural option.}
\tsnote{What is a ``query''?  A predicate? A
real-valued function? A (potentially) randomized algorithm?} \jnote{A query is a deterministic
function.}
\end{definition}

Our treatment of $\pub, M$ is not symmetric, since we only count $M$ against the size
of the data structure. When we define security
we may give the attacker $\pub$ but not~$M$, and in that case the data structure cannot
trivially make everything part of~$\pub$. \tsnote{Is the idea that
  anything that is secret is part of~$M$?  For example, if the scheme
  uses public hash functions to populate a bit-array, and then a
  secretly-keyed blockcipher to encipher the array; the
  blockcipher key is encoded in~$M$?  This may cause some issues in
  the security definitions, i.e.\ whether we can give~$M$ to the
  attacker or not. } \jnote{Yes, anything secret is part of $M$; anything public
  is part of $\pub$.} \tsnote{By the way, I'm coming around to the
  viewpoint that it is fair to include in the ``size'' of the
  representation any secret information.  In makes more difficult
  comparisons to classical lower-bounds (which [NY] makes, incorrectly
IMO), but it does seem fair to say ``this is how many bits of memory
you need to allocate to represent this set \emph{securely}.''}

It is not hard to see Bloom filters are one possible instantiation of the above. If we fix some
size bound~$n$, then $\mathcal{S}$ becomes the collection of all subsets of $U$
of size (at most)~$n$. We also fix $\mathcal{Q} = U$, where a query ``$x$'' has
the semantics ``is $x$ in $S$?'' Algorithm $\Rep$, which has values $k, m$ hardwired,
chooses a set of hash functions $h_1, \ldots, h_k$ and computes an $m$-bit
array in the usual way; a natural possibility is to set $\pub = (h_1, \ldots, h_k)$ and
to let $M$ be the bit array.  \tsnote{If $\mathcal{Q}=U$ and we use the
  semantics you suggest, then isn't Equation~\ref{eqn:correctness}
  both correctness and soundness?  If so, I don't see how this
  captures the classical BF, which requires $\epsilon=0$ for one kind
  of error, but allows $\epsilon>0$ for the other. } \jnote{The definition does not distinguish
  between elements in the set (for which $q(S)=1$) or outside the set (for which
  $q(S)=0$). But a Bloom filter does satisfy Equation~\ref{eqn:correctness} in either case.}
  \jnote{In that sense, I am using ``soundness'' and ``correctness'' interchangeably here.}
  \jnote{I'm not tied to allowing false negatives when we specialize the definition to the case
  of set-membership queries. But in the abstract definition it seems unclear why one would choose
  some queries on which error is ok and other queries where error is not allowed. Though if one
  wanted to be general, one could simply have two (disjoint) sets of queries $\mathcal{Q}_1, \mathcal{Q}_2$
  where error is allowed on the former but not on the latter.}

@@

The notion of FP-security defined above captures the fp-prv notion for Bloom filters
if we put the hash
functions in $M$ (and thus increase the size of the data structure); it also captures the fp-pub
notion if we put the hash function in~$\pub$. \tsnote{Except that the win condition allows both
false-positives and false-negatives, given the correctness requirement
in the syntax.} \jnote{True. But if false negatives cannot occur at all (by design of
the data structure, not by definition of the primitive), then the attacker cannot hope to win
by finding a false negative.} It captures the fp-bb-pub notion in the
random-oracle model.

@@

\item An ``indistinguishability'' definition where either $S_0$ or $S_1$ is used, and the attacker
must determine which. Here the attacker is given $\pub$ but only oracle access to $\Qry$, and
it is disallowed from asking any query $q$ for which $q(S_0) \neq
q(S_1)$. \tsnote{How will the adversary know that a query satisfies
  this in (say) the case of the classical BF?  We can, of course,
enforce it in the experiment, but then our resource accounting risks
overcounting the number of queries.} \jnote{I was assuming the attacker knows $S_0, S_1$.}
\tsnote{Also, we need that, in general, $\pub$ itself
does not leak information about~$S_0$ vs.\ $S_1$. } \jnote{Sure, this would be implied
by the definition in this case.}
\end{enumerate}
